Rectangulotopes

### 2024-04-26 draft/rectangulotopes.tex
update caption figure 2

\begin{figure}
  \includegraphics[width=\textwidth]{rectangulations.pdf}
	\caption{Four rectangulations. The leftmost rectangulation is not weakly equivalent to any other. The rightmost three are weakly equivalent, but only the first two are strongly equivalent. Only the third one is diagonal.}
	\label{fig:rectequiv}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\textwidth]{rectangulations.pdf}
	\caption{Four rectangulations. The rightmost rectangulation is not weakly equivalent to any other. The leftmost three are weakly equivalent, but only the first two are strongly equivalent. Only the third one is diagonal.}
	\label{fig:rectequiv}
\end{figure}
